Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex

\subsection{Central Base Station}
{\color{red}\textbf{NOT COMPLETE}}
\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{basestation}
\end{center}
\caption{Central Base Station Hardware}
\label{fig:basestation}
\end{figure}

The central base station is the point of contact between the sensor network and the server. The data gathered by the Arduino Fio and Raspberry Pi sensors are routed to the base station via XBee radios. The base station, which is itself a Raspberry Pi, forwards the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station. The base station runs the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing Python scripts that take care of forwarding the data via HTTP to the server was simple.

\subsection{Server Processing}
Once an image has been captured by an Acquisition Raspberry Pi it is transmitted via the XBee radio to the base station Raspberry Pi where it is uploaded online via an Ethernet connection. The REST route that the image is posted serves several purposes. First, it authenticates the sender by checking for a username and password. The script then timestamps the image and saves it to a directory on the server not directly accessible from the web. Lastly, the script calls a function to invoke two different automatic license plate recognition (ALPR) programs and store the resulting character extraction to a MySQL database.

>>>>

\subsection{Central Base Station}
{\color{red}\textbf{NOT COMPLETE}}
\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{basestation}
\end{center}
\caption{Central Base Station Hardware}
\label{fig:basestation}
\end{figure}
The central base station is the point of contact between the sensor network and the server. The data gathered by the Arduino Fio and Raspberry Pi sensors are routed to the base station via XBee radios. The base station, which is itself a Raspberry Pi, forwards the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station. The base station runs the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing Python scripts that take care of forwarding the data via HTTP to the server was simple. The more difficult task was writing code to allow the base station Raspberry Pi to interface with the XBee radio, and listen for packets coming from the XBee attached to the Arduino Fio. The Python code that runs on the base station Raspberry Pi is listed in Appendix 2.

\subsection{Server Processing}
{\color{red}\textbf{NOT COMPLETE}}
Once an image has been captured by an Acquisition Raspberry Pi it is transmitted via the XBee radio to the base station Raspberry Pi, where it is uploaded to the server via an Ethernet connection. The REST route to which the image is posted serves several purposes. First, it authenticates the sender by checking for a username and password. The script then timestamps the image and saves it to a directory on the server not directly accessible from the web. Lastly, the script calls a function to invoke two different automatic license plate recognition (ALPR) programs and stores the resulting character extractions to a MySQL database.
